Hypercoercions and a Framework for Equivalence of Cast Calculi

### 2019-10-21 paper.tex
minor changes

To use our framework, users needs to prove that their cast representation
implements Lazy D Cast ADT (Definition~\ref{def:surely-lazyd}), a subset of 
Cast ADT. Property (1) 
states that $id(T)$acts like the identity function. Property (2) states 
that $seq(c,c)$acts like a sequence of casts. Properties (3) through 
(11) state that $cast(T_1,l,T_2)$act like the Lazy D $applyCast$
defined in Fig.~\ref{fig:applyCast-D-C}.

\todoKC{define values before Lazy D Cast ADT}

>>>>

To use our framework, users needs to prove that their cast representation
implements Lazy D Cast ADT (Definition~\ref{def:surely-lazyd}), a subset of 
Cast ADT. Property (1) 
states that $id(T)$ acts like the identity function. Property (2) states 
that $seq(c,c)$ acts like a sequence of casts. Properties (3) through 
(11) state that $cast(T_1,l,T_2)$ act like the Lazy D $applyCast$
(Fig.~\ref{fig:applyCast-D-C}).

\todo[inline]{We might need to values before Lazy D Cast ADT.}
